---
title: "07May_Report"
output:
  html_document:
    keep_md: yes
    toc: yes
---
## Prime Minister After General Election
```{r, echo=FALSE,warning=FALSE}
library(ggplot2)
data <- read.table(
    "../../Betfair_UKPolitics_Odds_History.csv", 
    sep = ",",header = TRUE, stringsAsFactor = FALSE)

data$date <- 
    strptime(data$date_char, "%d/%m/%Y %H:%M:%s")
```
```{r,echo=FALSE}
local_data <- 
    data[data$Market == "2015 UK General Election - Prime Minister After General Election",]

local_data <- local_data[local_data$date > strptime("2015-05-07", format = "%Y-%m-%d"),]

local_data <- local_data[local_data$Outcome %in% c("David Cameron", "Ed Miliband"),]

local_data <- local_data[!is.na(local_data$Outcome),]
local_data$ymax <- 1/local_data$Back
local_data$ymin <- 1/local_data$Lay
local_data[is.na(local_data$ymax),"ymax"] <- 1 
local_data[is.na(local_data$ymin),"ymin"] <- 0
local_data$Prob <- (local_data$ymax + local_data$ymin)/2


ggplot(data = local_data, aes(x = date , y = Prob * 100, colour = Outcome)) + 
    geom_line() +
    facet_grid(. ~ Market) +
    ylab("(implied) probability (%)") +
    geom_errorbar(aes(ymin = ymin * 100, ymax = ymax * 100)) 
```

## Next Government
```{r,echo=FALSE}
local_data <- 
    data[data$Market == "2015 UK General Election - Next Government",]

local_data <- local_data[local_data$date > strptime("2015-05-07", format = "%Y-%m-%d"),]

local_data <- local_data[!is.na(local_data$Outcome),]
local_data$ymax <- 1/local_data$Back
local_data$ymin <- 1/local_data$Lay
local_data[is.na(local_data$ymax),"ymax"] <- 1 
local_data[is.na(local_data$ymin),"ymin"] <- 0
local_data$Prob <- (local_data$ymax + local_data$ymin)/2


ggplot(data = local_data, aes(x = date , y = Prob * 100, colour = Outcome)) + 
    geom_line() +
    facet_grid(. ~ Market) +
    ylab("(implied) probability (%)") +
    geom_errorbar(aes(ymin = ymin * 100, ymax = ymax * 100)) 
```

## South Thanet
```{r,echo=FALSE}
local_data <- 
    data[data$Market == "South Thanet - Winner",]

local_data <- local_data[local_data$date > strptime("2015-05-07", format = "%Y-%m-%d"),]

local_data <- local_data[!is.na(local_data$Outcome),]
local_data$ymax <- 1/local_data$Back
local_data$ymin <- 1/local_data$Lay
local_data[is.na(local_data$ymax),"ymax"] <- 1 
local_data[is.na(local_data$ymin),"ymin"] <- 0
local_data$Prob <- (local_data$ymax + local_data$ymin)/2


ggplot(data = local_data, aes(x = date , y = Prob * 100, colour = Outcome)) + 
    geom_line() +
    facet_grid(. ~ Market) +
    ylab("(implied) probability (%)") +
    geom_errorbar(aes(ymin = ymin * 100, ymax = ymax * 100)) 
```

## UKIP Seats Total
```{r,echo=FALSE}
local_data <- 
    data[data$Market == "UK Seat Totals - UKIP Seats Total",]

local_data <- local_data[local_data$date > strptime("2015-05-07", format = "%Y-%m-%d"),]

local_data <- local_data[!is.na(local_data$Outcome),]
local_data$ymax <- 1/local_data$Back
local_data$ymin <- 1/local_data$Lay
local_data[is.na(local_data$ymax),"ymax"] <- 1 
local_data[is.na(local_data$ymin),"ymin"] <- 0
local_data$Prob <- (local_data$ymax + local_data$ymin)/2


ggplot(data = local_data, aes(x = date , y = Prob * 100, colour = Outcome)) + 
    geom_line() +
    facet_grid(. ~ Market) +
    ylab("(implied) probability (%)") +
    geom_errorbar(aes(ymin = ymin * 100, ymax = ymax * 100)) 
```

## Overall Majority
```{r,echo=FALSE}
local_data <- 
    data[data$Market == "2015 UK General Election - Overall Majority",]

local_data <- local_data[local_data$date > strptime("2015-05-07", format = "%Y-%m-%d"),]

local_data <- local_data[!is.na(local_data$Outcome),]
local_data$ymax <- 1/local_data$Back
local_data$ymin <- 1/local_data$Lay
local_data[is.na(local_data$ymax),"ymax"] <- 1 
local_data[is.na(local_data$ymin),"ymin"] <- 0
local_data$Prob <- (local_data$ymax + local_data$ymin)/2


ggplot(data = local_data, aes(x = date , y = Prob * 100, colour = Outcome)) + 
    geom_line() +
    facet_grid(. ~ Market) +
    ylab("(implied) probability (%)") +
    geom_errorbar(aes(ymin = ymin * 100, ymax = ymax * 100)) 
```

## Most Seats
```{r,echo=FALSE}
local_data <- 
    data[data$Market == "2015 UK General Election - Most Seats",]

local_data <- local_data[local_data$date > strptime("2015-05-07", format = "%Y-%m-%d"),]

local_data <- local_data[!is.na(local_data$Outcome),]
local_data$ymax <- 1/local_data$Back
local_data$ymin <- 1/local_data$Lay
local_data[is.na(local_data$ymax),"ymax"] <- 1 
local_data[is.na(local_data$ymin),"ymin"] <- 0
local_data$Prob <- (local_data$ymax + local_data$ymin)/2


ggplot(data = local_data, aes(x = date , y = Prob * 100, colour = Outcome)) + 
    geom_line() +
    facet_grid(. ~ Market) +
    ylab("(implied) probability (%)") +
    geom_errorbar(aes(ymin = ymin * 100, ymax = ymax * 100)) 
```

## UKIP Under/Over 2.5 Seats
```{r,echo=FALSE}
local_data <- 
    data[data$Market == "UK Seat Totals - UKIP U/O 2.5 Seats",]

local_data <- local_data[local_data$date > strptime("2015-05-07", format = "%Y-%m-%d"),]

local_data <- local_data[!is.na(local_data$Outcome),]
local_data$ymax <- 1/local_data$Back
local_data$ymin <- 1/local_data$Lay
local_data[is.na(local_data$ymax),"ymax"] <- 1 
local_data[is.na(local_data$ymin),"ymin"] <- 0
local_data$Prob <- (local_data$ymax + local_data$ymin)/2


ggplot(data = local_data, aes(x = date , y = Prob * 100, colour = Outcome)) + 
    geom_line() +
    facet_grid(. ~ Market) +
    ylab("(implied) probability (%)") +
    geom_errorbar(aes(ymin = ymin * 100, ymax = ymax * 100)) 
```

## UKIP Seats 2
```{r,echo=FALSE}
local_data <- 
    data[data$Market == "UK Seat Totals - UKIP Seats Total 2",]

local_data <- local_data[local_data$date > strptime("2015-05-07", format = "%Y-%m-%d"),]

local_data <- local_data[!is.na(local_data$Outcome),]
local_data$ymax <- 1/local_data$Back
local_data$ymin <- 1/local_data$Lay
local_data[is.na(local_data$ymax),"ymax"] <- 1 
local_data[is.na(local_data$ymin),"ymin"] <- 0
local_data$Prob <- (local_data$ymax + local_data$ymin)/2


ggplot(data = local_data, aes(x = date , y = Prob * 100, colour = Outcome)) + 
    geom_line() +
    facet_grid(. ~ Market) +
    ylab("(implied) probability (%)") +
    geom_errorbar(aes(ymin = ymin * 100, ymax = ymax * 100)) 
```

## Conservative Seats
```{r,echo=FALSE}
local_data <- 
    data[data$Market == "UK Seat Totals - Conservative Seats Total",]

local_data <- local_data[local_data$date > strptime("2015-05-07", format = "%Y-%m-%d"),]

local_data <- local_data[!is.na(local_data$Outcome),]
local_data$ymax <- 1/local_data$Back
local_data$ymin <- 1/local_data$Lay
local_data[is.na(local_data$ymax),"ymax"] <- 1 
local_data[is.na(local_data$ymin),"ymin"] <- 0
local_data$Prob <- (local_data$ymax + local_data$ymin)/2


ggplot(data = local_data, aes(x = date , y = Prob * 100, colour = Outcome)) + 
    geom_line() +
    facet_grid(. ~ Market) +
    ylab("(implied) probability (%)") +
    geom_errorbar(aes(ymin = ymin * 100, ymax = ymax * 100)) 
```

## Lib Dem Seats
```{r,echo=FALSE}
local_data <- 
    data[data$Market == "UK Seat Totals - Lib Dem Seats Total",]

local_data <- local_data[local_data$date > strptime("2015-05-07", format = "%Y-%m-%d"),]

local_data <- local_data[!is.na(local_data$Outcome),]
local_data$ymax <- 1/local_data$Back
local_data$ymin <- 1/local_data$Lay
local_data[is.na(local_data$ymax),"ymax"] <- 1 
local_data[is.na(local_data$ymin),"ymin"] <- 0
local_data$Prob <- (local_data$ymax + local_data$ymin)/2


ggplot(data = local_data, aes(x = date , y = Prob * 100, colour = Outcome)) + 
    geom_line() +
    facet_grid(. ~ Market) +
    ylab("(implied) probability (%)") +
    geom_errorbar(aes(ymin = ymin * 100, ymax = ymax * 100)) 
```

## Electoral Bias
```{r,echo=FALSE}
local_data <- 
    data[data$Market == "2015 UK General Election - Electoral Bias",]

local_data <- local_data[local_data$date > strptime("2015-05-07", format = "%Y-%m-%d"),]

local_data <- local_data[!is.na(local_data$Outcome),]
local_data$ymax <- 1/local_data$Back
local_data$ymin <- 1/local_data$Lay
local_data[is.na(local_data$ymax),"ymax"] <- 1 
local_data[is.na(local_data$ymin),"ymin"] <- 0
local_data$Prob <- (local_data$ymax + local_data$ymin)/2


ggplot(data = local_data, aes(x = date , y = Prob * 100, colour = Outcome)) + 
    geom_line() +
    facet_grid(. ~ Market) +
    ylab("(implied) probability (%)") +
    geom_errorbar(aes(ymin = ymin * 100, ymax = ymax * 100)) 
```

## Labour Seats
```{r,echo=FALSE}
local_data <- 
    data[data$Market == "UK Seat Totals - Labour Seats Total",]

local_data <- local_data[local_data$date > strptime("2015-05-07", format = "%Y-%m-%d"),]

local_data <- local_data[!is.na(local_data$Outcome),]
local_data$ymax <- 1/local_data$Back
local_data$ymin <- 1/local_data$Lay
local_data[is.na(local_data$ymax),"ymax"] <- 1 
local_data[is.na(local_data$ymin),"ymin"] <- 0
local_data$Prob <- (local_data$ymax + local_data$ymin)/2


ggplot(data = local_data, aes(x = date , y = Prob * 100, colour = Outcome)) + 
    geom_line() +
    facet_grid(. ~ Market) +
    ylab("(implied) probability (%)") +
    geom_errorbar(aes(ymin = ymin * 100, ymax = ymax * 100)) 
```

## Voter Turnout
```{r,echo=FALSE}
local_data <- 
    data[data$Market == "2015 General Election - Registered Voter Turnout",]

local_data <- local_data[local_data$date > strptime("2015-05-07", format = "%Y-%m-%d"),]

local_data <- local_data[!is.na(local_data$Outcome),]
local_data$ymax <- 1/local_data$Back
local_data$ymin <- 1/local_data$Lay
local_data[is.na(local_data$ymax),"ymax"] <- 1 
local_data[is.na(local_data$ymin),"ymin"] <- 0
local_data$Prob <- (local_data$ymax + local_data$ymin)/2


ggplot(data = local_data, aes(x = date , y = Prob * 100, colour = Outcome)) + 
    geom_line() +
    facet_grid(. ~ Market) +
    ylab("(implied) probability (%)") +
    geom_errorbar(aes(ymin = ymin * 100, ymax = ymax * 100)) 
```

## Two General Elections 2015?
```{r,echo=FALSE}
local_data <- 
    data[data$Market == "2015 UK General Election - Two General Elections 2015??",]

local_data <- local_data[local_data$date > strptime("2015-05-07", format = "%Y-%m-%d"),]

local_data <- local_data[!is.na(local_data$Outcome),]
local_data$ymax <- 1/local_data$Back
local_data$ymin <- 1/local_data$Lay
local_data[is.na(local_data$ymax),"ymax"] <- 1 
local_data[is.na(local_data$ymin),"ymin"] <- 0
local_data$Prob <- (local_data$ymax + local_data$ymin)/2


ggplot(data = local_data, aes(x = date , y = Prob * 100, colour = Outcome)) + 
    geom_line() +
    facet_grid(. ~ Market) +
    ylab("(implied) probability (%)") +
    geom_errorbar(aes(ymin = ymin * 100, ymax = ymax * 100)) 
```

## Conservative Under/Over 278.5 Seats
```{r,echo=FALSE}
local_data <- 
    data[data$Market == "UK Seat Totals - Conservative U/O 278.5 Seats",]

local_data <- local_data[local_data$date > strptime("2015-05-07", format = "%Y-%m-%d"),]

local_data <- local_data[!is.na(local_data$Outcome),]
local_data$ymax <- 1/local_data$Back
local_data$ymin <- 1/local_data$Lay
local_data[is.na(local_data$ymax),"ymax"] <- 1 
local_data[is.na(local_data$ymin),"ymin"] <- 0
local_data$Prob <- (local_data$ymax + local_data$ymin)/2


ggplot(data = local_data, aes(x = date , y = Prob * 100, colour = Outcome)) + 
    geom_line() +
    facet_grid(. ~ Market) +
    ylab("(implied) probability (%)") +
    geom_errorbar(aes(ymin = ymin * 100, ymax = ymax * 100)) 
```

## SNP Seats 
```{r,echo=FALSE}
local_data <- 
    data[data$Market == "UK Seat Totals - SNP Seats Total 2",]

local_data <- local_data[local_data$date > strptime("2015-05-07", format = "%Y-%m-%d"),]

local_data <- local_data[!is.na(local_data$Outcome),]
local_data$ymax <- 1/local_data$Back
local_data$ymin <- 1/local_data$Lay
local_data[is.na(local_data$ymax),"ymax"] <- 1 
local_data[is.na(local_data$ymin),"ymin"] <- 0
local_data$Prob <- (local_data$ymax + local_data$ymin)/2


ggplot(data = local_data, aes(x = date , y = Prob * 100, colour = Outcome)) + 
    geom_line() +
    facet_grid(. ~ Market) +
    ylab("(implied) probability (%)") +
    geom_errorbar(aes(ymin = ymin * 100, ymax = ymax * 100)) 
```

## LibDem Seats Under/Over 32.5 Seats
```{r,echo=FALSE}
local_data <- 
    data[data$Market == "UK Seat Totals - Lib Dem U/O 32.5 Seats",]

local_data <- local_data[local_data$date > strptime("2015-05-07", format = "%Y-%m-%d"),]

local_data <- local_data[!is.na(local_data$Outcome),]
local_data$ymax <- 1/local_data$Back
local_data$ymin <- 1/local_data$Lay
local_data[is.na(local_data$ymax),"ymax"] <- 1 
local_data[is.na(local_data$ymin),"ymin"] <- 0
local_data$Prob <- (local_data$ymax + local_data$ymin)/2


ggplot(data = local_data, aes(x = date , y = Prob * 100, colour = Outcome)) + 
    geom_line() +
    facet_grid(. ~ Market) +
    ylab("(implied) probability (%)") +
    geom_errorbar(aes(ymin = ymin * 100, ymax = ymax * 100)) 
```

## Conservative Seats Under/Over 287.5 Seats
```{r,echo=FALSE}
local_data <- 
    data[data$Market == "UK Seat Totals - Conservative U/O 287.5 Seats",]

local_data <- local_data[local_data$date > strptime("2015-05-07", format = "%Y-%m-%d"),]

local_data <- local_data[!is.na(local_data$Outcome),]
local_data$ymax <- 1/local_data$Back
local_data$ymin <- 1/local_data$Lay
local_data[is.na(local_data$ymax),"ymax"] <- 1 
local_data[is.na(local_data$ymin),"ymin"] <- 0
local_data$Prob <- (local_data$ymax + local_data$ymin)/2


ggplot(data = local_data, aes(x = date , y = Prob * 100, colour = Outcome)) + 
    geom_line() +
    facet_grid(. ~ Market) +
    ylab("(implied) probability (%)") +
    geom_errorbar(aes(ymin = ymin * 100, ymax = ymax * 100)) 
```

## Labour Seats Scotland
```{r,echo=FALSE}
local_data <- 
    data[data$Market == "Scotland - Labour Seats Scotland",]

local_data <- local_data[local_data$date > strptime("2015-05-07", format = "%Y-%m-%d"),]

local_data <- local_data[!is.na(local_data$Outcome),]
local_data$ymax <- 1/local_data$Back
local_data$ymin <- 1/local_data$Lay
local_data[is.na(local_data$ymax),"ymax"] <- 1 
local_data[is.na(local_data$ymin),"ymin"] <- 0
local_data$Prob <- (local_data$ymax + local_data$ymin)/2


ggplot(data = local_data, aes(x = date , y = Prob * 100, colour = Outcome)) + 
    geom_line() +
    facet_grid(. ~ Market) +
    ylab("(implied) probability (%)") +
    geom_errorbar(aes(ymin = ymin * 100, ymax = ymax * 100)) 
```



