---
title: "Betfair_UKPolitics"
output:
  html_document:
    keep_md: yes
    toc: yes
---

# About

I am interested in *UK Political Betting*. so, I regularly get odds from all Betfair's "UK Politics" Markets, i.e. all the sub-branches of [this page](http://www.betfair.com/exchange/?nodeId=MENU:2707982).

This Project if about Getting, Cleaning, and Exploratory Analysis of those odds.

\newpage  

# Preparing Data

## Getting List of Betfair UK Politics Markets

*Get_list_of_Betfair_UKPolitics_Markets.R* recursively retrives a list of all the market that [this page](http://www.betfair.com/exchange/?nodeId=MENU:2707982) is a parent or grandparent of.

As the markets don't appear (or disappear) everyday, I only run the following (commented out) chunk once or twice a week. 

```{r}
# root_dir <- getwd()
# setwd("./Codes/")
# source("Get_list_of_Betfair_UKPolitics_Markets.R")
# setwd(root_dir)
```

The output file looks like:
```{r}
list_of_markets<- 
    read.csv(
        "./raw_data/list_of_Betfair_UKPolitics_Markets.txt",
        header = FALSE)
head(list_of_markets)
num_markets <- dim(list_of_markets)[1]
```
There are `r num_markets` unique UK-Politics markets on Betfair.

## Getting Odds

A c# project goes through all `r num_markets` markets, parses HTMLs, extracts usefull bits, and appends them to the existing *Betfair_UKPolitics_odds.csv* file.

the output looks like:
```{r}
head(read.table("./raw_data/Betfair_UKPolitics_odds.csv", sep = "\t"))
```


